**The status of the microbial census: an update**

### 2016-01-18 doc/notebook/Bacterial_data_acquisition.Rmd
Split at class level instead of phylum

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur, seed=1);
	cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, splitmethod=classify, classic=T, taxlevel=2, cluster=F, processors=12)
	cluster.split(file=all_bacteria.filter.unique.precluster.file, processors=8, classic=TRUE)"
```

>>>>

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur, seed=1);
	cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, splitmethod=classify, classic=T, taxlevel=3, cluster=F, processors=12)
	cluster.split(file=all_bacteria.filter.unique.precluster.file, processors=8, classic=TRUE)"
```
